|

### 2020-06-15 appendix/appendix_final.Rmd
commit final appendix 06/14
commit app 06/15 1

## Geographical Location

The geographical location also varies considerably in the sample. In our sampled papers, `r as.numeric(table(unique(select(dat, id, location2))$location2)[1])` studied a given country, while `r as.numeric(table(unique(select(dat, id, location2))$location2)[2])` used a cross-country design, with more than one country.

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Geographical Location"}
dat %>%
  select(id, location2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(location2))) + 
    geom_bar(color = "black") + 
  labs(x = "Geographical Location",
       y = "") + 
  theme_bw()
```

@@

```{r, echo=F,warning=F,message=F}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c('Other Coefficients', 'Main Coefficients')
aux <- select(fulldat, usemeta2, indepvar2, year, published, 
              elecsys2, method, agglevel, location2) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year, 
         `Published work` = published, 
         `Electoral system` = elecsys2, 
         `Estimation method` = method, 
         `Sampling Aggregation Level` = agglevel, 
         `Sample Location` = location2)

@@

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)

mod1 <- tibble(
     ` ` = c("Intercept", 
             "Indepvar: N", 
             "Indepvar: logN", 
             "Year", 
             "Published: No",
             "Elecsys: Non-Majoritarian", 
             "Method: Panel", 
             "AggLevel: States", 
             "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ", 
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))
```

@@

mod1_permu <- tibble(
     ` ` = c("Intercept", 
             "Indepvar: N", 
             "Indepvar: logN", 
             "Year", 
             "Published: No", 
             "Elecsys: Non-Majoritarian", 
             "Method: Panel", 
             "AggLevel: States", 
             "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3))) 
```

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)

mod2 <- tibble(
  ` ` = c("Intercept", 
          "Indepvar: N", 
          "Indepvar: logN", 
          "Year", 
          "Published: No",
          "Elecsys: Non-Majoritarian", 
          "Method: Panel", 
          "AggLevel: States", 
          "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3))) 
```

@@

mod2_permu <- tibble(
     ` ` = c("Intercept", 
             "Indepvar: N", 
             "Indepvar: logN", 
             "Year", 
             "Published: No",
             "Elecsys: Non-Majoritarian", 
             "Method: Panel", 
             "AggLevel: States", 
             "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear)

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)

mod4 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod4_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)

@@

```{r, echo=F, warning=F, error=F, message=F}
coefs <- tibble(
  ` ` = c("Intercept", 
          "Indepvar: N",
          "Indepvar: logN", 
          "Year", 
          "Published: No", 
          "Elecsys: Non-Majoritarian",
          "Method: Panel", 
          "Method: IV", 
          "Method: RDD", 
          "AggLevel: States", 
          "Location: World"))

aux = list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order),
         order = ifelse(` ` == "Location: World", 11, order)) %>%
  filter(` ` != "Method: RDD") %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~(ifelse(is.na(.), " ", .)))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order),
         order = ifelse(` ` == "Location: World", 11, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

@@

```{r, echo=F, warning=F,error=F,message=F}
coefs <- tibble(
  ` ` = c("Intercept", 
          "Indepvar: N",
          "Indepvar: logN", 
          "Year", 
          "Published: No", 
          "Elecsys: Non-Majoritarian",
          "Method: Panel", 
          "Method: IV", 
          "Method: RDD", 
          "AggLevel: States", 
          "Location: World")
)

aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order),
         order = ifelse(` ` == "Location: World", 11, order)) %>%
  arrange(order) %>%
  filter(` ` != "Method: RDD") %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order),
         order = ifelse(` ` == "Location: World", 11, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

@@

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha")
```

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha")
```

@@

This function is for building a forest plot using `ggplot2` from meta analysis dataset.

>>>>

@@

```{r, echo=F,warning=F,message=F}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c('Other Coefficients', 'Main Coefficients')
aux <- select(fulldat, usemeta2, indepvar2, year, published, 
              elecsys2, method, agglevel) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year, 
         `Published work` = published, 
         `Electoral system` = elecsys2, 
         `Estimation method` = method, 
         `Sampling Aggregation Level` = agglevel)

@@

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel, 
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)

mod1 <- tibble(
     ` ` = c("Intercept", 
             "Indepvar: N", 
             "Indepvar: logN", 
             "Year", 
             "Published: No",
             "Elecsys: Non-Majoritarian", 
             "Method: Panel", 
             "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ", 
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))
```

@@

mod1_permu <- tibble(
     ` ` = c("Intercept", 
             "Indepvar: N", 
             "Indepvar: logN", 
             "Year", 
             "Published: No", 
             "Elecsys: Non-Majoritarian", 
             "Method: Panel", 
             "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3))) 
```

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel, 
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)

mod2 <- tibble(
  ` ` = c("Intercept", 
          "Indepvar: N", 
          "Indepvar: logN", 
          "Year", 
          "Published: No",
          "Elecsys: Non-Majoritarian", 
          "Method: Panel", 
          "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3))) 
```

@@

mod2_permu <- tibble(
     ` ` = c("Intercept", 
             "Indepvar: N", 
             "Indepvar: logN", 
             "Year", 
             "Published: No",
             "Elecsys: Non-Majoritarian", 
             "Method: Panel", 
             "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel, 
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear)

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel, 
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)

mod4 <- tibble(
  ` ` = c("Intercept", 
          "Indepvar: N", 
          "Year", 
          "Elecsys: Non-Majoritarian",
          "Method: Panel", 
          "Method: IV" ,
          "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod4_permu <- tibble(
  ` ` = c("Intercept", 
          "Indepvar: N", 
          "Year", 
          "Elecsys: Non-Majoritarian",
          "Method: Panel", 
          "Method: IV", 
          "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel, 
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel, 
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)

@@

```{r, echo=F, warning=F, error=F, message=F}
coefs <- tibble(
  ` ` = c("Intercept", 
          "Indepvar: N",
          "Indepvar: logN", 
          "Year", 
          "Published: No", 
          "Elecsys: Non-Majoritarian",
          "Method: Panel", 
          "Method: IV", 
          "Method: RDD", 
          "AggLevel: States"))

aux = list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
  filter(` ` != "Method: RDD") %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~(ifelse(is.na(.), " ", .)))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

@@

```{r, echo=F, warning=F,error=F,message=F}
coefs <- tibble(
  ` ` = c("Intercept", 
          "Indepvar: N",
          "Indepvar: logN", 
          "Year", 
          "Published: No", 
          "Elecsys: Non-Majoritarian",
          "Method: Panel", 
          "Method: IV", 
          "Method: RDD", 
          "AggLevel: States")
)

aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
  arrange(order) %>%
  filter(` ` != "Method: RDD") %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

@@

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel, 
              test = "knha")
```

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel, 
              test = "knha")
```

@@

This function receives the meta-analysis results and build a forest plot using `ggplot2`.
